TADCompare: an R package for differential analysis and characterization of Topologically Associated Domains

### 2019-11-05 manuscript/manuscript.Rmd
Add Availability of data and materials section
Adjust abbreviations and contributions

@@

- GWAS - Genome-Wide Association Study
- KEGG - Kyoto Encyclopedia of Genes and Genomes
- MSigDb - Molecular Signatures Database 
- PPI - Protein-Protein Interaction
- SNP - Single Nucleotide Polymorphism

@@

>>>>

## Availability of data and materials

The code and the data supporting the conclusions of this article are available in the https://github.com/dozmorovlab/disease_coherence GitHub repository.

@@

GWAS - Genome-Wide Association Study; KEGG - Kyoto Encyclopedia of Genes and Genomes; MSigDb - Molecular Signatures Database; PPI - Protein-Protein Interaction; SNP - Single Nucleotide Polymorphism

@@

## Authors’ contributions

MD, KK, CC, and MR conceived the study. KC and MD performed the experiments. MD primarily wrote the manuscript. KK, MR, CC, and SB participated in manuscript writing. All authors read and approved the final manuscript.
